Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/methodology.tex
Killed orphans dead.

The purpose of these questions was to determine how upset participants would be when data is inappropriately shared, and to understand how their reaction depends upon the type and recipient of the data that is shared. Thus, our question pool consisted of 293 questions: the 288 described here, plus 5 that we describe in the next section. In this section of the survey, participants received six questions, randomly drawn from this pool.

>>>>

The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Each participant answered 6 questions that were randomly drawn from a pool of 293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).
